---
title: "Plotly Assignment"
author: "STP"
date: "12/21/2020"
output: html_document
---

```{r setup, results = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(plotly)
library(dplyr)
```

## Plotly Assignment

This assignment creates an interactive plot using Plotly. It will use the state data sets that are part of the R Datasets Package. This data set includes the mean number of days with minimum temperatures below freezing, and this will be integrated into the Plotly plot. 

```{r look at data set}
head(state.x77)

```


```{r create data frame}

# Create data frame
state_frost <- data.frame(State = state.abb, Frost = as.vector(state.x77[,7]))

```



```{r create the plot}

# Create hover text
state_frost$hover <- with(state_frost, paste(State, '<br>', "Days of Frost:", Frost))
# Make state borders red
borders <- list(color = toRGB("red"))
# Set up some mapping options
map_options <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)
# makes the plot
plot_ly(z = ~state_frost$Frost, text = ~state_frost$hover, locations = ~state_frost$State, 
       type = 'choropleth', locationmode = 'USA-states', 
       color = state_frost$Frost, colors = 'Blues', marker = list(line = borders)) %>%
  layout(title = 'US Mean Days of Frost 1931-1960', geo = map_options)

```

Figure 1. This map indicates the mean number of days below freezing in each of the US states from 1931-1960.